---
title: "Activity Monitoring_Rcourse"
output: html_document
---

```{r Loading & Preprocessing}
activity <- read.csv("~/Downloads/activity.csv")
str(activity)
activity$Date <- strptime(as.character(activity$date),"%Y-%m-%d")
class(activity$Date) 

```


````{r Mean total number of steps taken}
totalSteps <- with(activity,tapply(steps,date,sum))
hist(totalSteps)

summary(totalSteps)

````

The mean and median total number of steps taken per day are:  
- Mean: 10770  
- Median: 10760

````{r Average daily activity pattern}

activity$step_average <- with(activity,tapply(steps,interval,mean,na.rm=TRUE))
str(activity$step_average)
with(activity,plot(interval,step_average,type="l"))

activity$interval[max(activity$step_average)]

````

The interval with the maximum number of steps is at 1705

````{r Mising values}

activity$steps2 <- activity$steps
activity$steps2[is.na(activity$steps2)] <- activity$step_average[is.na(activity$steps2)]
str(activity)


totalSteps2 <- with(activity,tapply(steps2,date,sum))
hist(totalSteps2)
summary(totalSteps2)

````

1. Total number of missing values: 2304
2.  The column "steps2" is the same as steps but with the NA replaced with the means of that particular 5-minute interval
3. The new mean & median is 10770. Compared to the first part of the assignment, the median is now the same as the mean.

```{r Weekdays & weekends}

activity$weekday <- weekdays(activity$Date)
activity$weekday <- ifelse(activity$weekday %in% c("Saturday", "Sunday"), c("weekend"), c("weekday"))
table(activity$weekday)

library(ggplot2)

activity$step_average2 <- with(activity,tapply(steps2,interval,mean,na.rm=TRUE))
qplot(interval, step_average2, data=activity, facets= weekday~., geom="line")
